Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-14 docs/google-research-awards-latam/main.tex
update paper results

%% \section{Related Work}
%% \Mar{rule of thumb: explain the
%%   contribution/novelty, then results achieved, and then how it relates
%% with our proposal.}
%% \Mar{this is not clear$\rightarrow$}Yang et al. \cite{yang-2011-finding} proposed CSmith\footnote{\url{http://embed.cs.utah.edu/csmith/}}, a grammar-fuzzer 
%% of C programs to generate invalid entries\Fix{the goal of a
%%    fuzzer is to generate valid inputs/entries. this is strange}\MAB{the
%%   goal is to generate valid programs without undefined behavior to
%%   facilitate differential testing} and
%% find bugs in several C compilers\Fix{it is strange that you don't mention differential
%%   testing, which is central in CSmith, and the use of LLVM and GCC as
%%   oracles.}.\Mar{this is just listing fuzzers. don't do this. try to
%%   follow rule of thumb above.}Similar fuzzers involving grammar and rules are found in Holler et al. \cite{holler-2012-fuzzing} 
%% that exposes the LangFuzz to generate entries based in code fragments 
%% (language grammar, sample code, test suite) and the tool Mozilla 
%% Funfuzz\footnote{\url{https://github.com/MozillaSecurity/funfuzz}}
%% that implements a fuzzer based on JavaScript language to improve the 
%% testing for SpiderMonkey engine, the interpreter of Mozilla Firefox.
%% \Fix{...}

@@

The basic workflow described in Section~\ref{sec:design} is functional. This section shows preliminary
results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is
promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
issue trackers of different engines in the period of a month. For
example, bug \# 6 was manifested by the JS code \CodeIn{var a =
  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
  === 0)\}}\footnote{This is a Lithium-minimized~\cite{lithium}
  version of the fuzzed code.}. In the original version of this code, the \CodeIn{valueOf} function returned
the empty string, whose integer representation, according to the spec,
should be zero\Fix{igor, please look for the part of spec and add link}. The modified
code returns a string representation of an invalid hexadecimal
value\Fix{igor, how do we know this is invalid?}. As such, the engines
are not expected to evaluate that string at the assertion expression;
hence test execution is expected to fail. Chakra,
however, is able to parse the string as a number. It returns a null
object, which is then converted to zero, making the test to pass.
\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
  \vspace{-2ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    10, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        & \checkm &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
   \bottomrule     
  \end{tabular}
\end{wraptable}

>>>>

% \section{Related Work}
% Differential testing with fuzzing can improve the quality of programs
% Yang et al. \cite{yang-2011-finding}

%% \Mar{rule of thumb: explain the
%%   contribution/novelty, then results achieved, and then how it relates
%% with our proposal.}
%% \Mar{this is not clear$\rightarrow$}Yang et al. \cite{yang-2011-finding} proposed CSmith\footnote{\url{http://embed.cs.utah.edu/csmith/}}, a grammar-fuzzer 
%% of C programs to generate invalid entries\Fix{the goal of a
%%    fuzzer is to generate valid inputs/entries. this is strange}\MAB{the
%%   goal is to generate valid programs without undefined behavior to
%%   facilitate differential testing} and
%% find bugs in several C compilers\Fix{it is strange that you don't mention differential
%%   testing, which is central in CSmith, and the use of LLVM and GCC as
%%   oracles.}.\Mar{this is just listing fuzzers. don't do this. try to
%%   follow rule of thumb above.}Similar fuzzers involving grammar and rules are found in Holler et al. \cite{holler-2012-fuzzing} 
%% that exposes the LangFuzz to generate entries based in code fragments 
%% (language grammar, sample code, test suite) and the tool Mozilla 
%% Funfuzz\footnote{\url{https://github.com/MozillaSecurity/funfuzz}}
%% that implements a fuzzer based on JavaScript language to improve the 
%% testing for SpiderMonkey engine, the interpreter of Mozilla Firefox.
%% \Fix{...}

@@

The basic workflow described in Section~\ref{sec:design} is functional. This section shows preliminary
results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is
promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
issue trackers of different engines in the period of a month. For
example, bug \# 6 was manifested by the JS code \CodeIn{var a =
  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
  === 0)\}}\footnote{This is a Lithium-minimized~\cite{lithium}
  version of the fuzzed code.}. In the original version of this code 
  \Igor{this code is the original fuzzed code, not the minimized version. we can use just (+``\textbackslash{}x00''===0)}, 
  the \CodeIn{valueOf} function returned
the empty string, whose integer representation, according to the spec of Unary Plus\cite{unary-plus},
should be zero. The modified
code returns a string representation of an invalid hexadecimal
value\Fix{igor, how do we know this is invalid?}\Igor{0x00 = NULL terminator \url{http://www.asciitable.com}, but is not a "null" keyword (+null is equal 0)}. As such, the engines
are not expected to evaluate that string at the assertion expression;
hence test execution is expected to fail. Chakra,
however, is able to parse the string as a number. It returns a null
object, which is then converted to zero, making the test to pass. \Igor{according the technical explanation:\\
the function String::toDouble should check the length, instead of null terminator. \url{https://github.com/Microsoft/ChakraCore/commit/98fbc297e2b2781bc4d6ed3ff360dba8d18c1eda}}
\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
  \vspace{-2ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    10, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        & \checkm &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
   \bottomrule     
  \end{tabular}
\end{wraptable}
